si: code and prose exploring Spatial Interaction models

### 2022-06-13 README.qmd
Change name, close #20

<!-- # Implementations in other languages -->
## si basics

@@

As documented in the [si vignette](https://robinlovelace.github.io/sim/articles/sim.html), the function allows you to use any variable in the origin or destination data by joining all attributes onto the OD data frame, with column names appended with `origin` and `destination`.

>>>>

<!-- # Implementations in other languages -->
## sim basics

@@

As documented in the [sim vignette](https://robinlovelace.github.io/sim/articles/sim.html), the function allows you to use any variable in the origin or destination data by joining all attributes onto the OD data frame, with column names appended with `origin` and `destination`.
